Matching bullets

### 2015-11-18 imaging-paper.Rnw
aspect ratio figure 2

\begin{figure}[hbtp]
  \centering
    \subfloat[View from the side.\label{fig:sidex3p}]{%
      \includegraphics[width=\linewidth]{images/sidex3p.png}
    }
    \hfill
    \subfloat[View from the top.\label{fig:topx3p}]{%
    \includegraphics[width=\linewidth]{images/topx3p.png}
    }
\caption{An example of a scan of a bullet land.}
\end{figure}
Each fired bullet is provided in form of a set of six x3p files, where each file is a surface scan between adjacent grooves on the bullet, called a ``land". An example of plotting one of these lands is given in Figures~\ref{fig:sidex3p} and~\ref{fig:topx3p}, which show side and top profiles of the land respectively.

>>>>

\begin{figure}[hbtp]
  \centering
    \subfloat[View from the side.\label{fig:sidex3p}]{%
      \includegraphics[width=\linewidth]{images/sidex3p.png}
    }
    \hfill
    \subfloat[View from the top.\label{fig:topx3p}]{%
    \includegraphics[width=\linewidth]{images/topx3p.png}
    }
\caption{An example of a scan of a bullet land. \hh{XXX is the code for these pictures somewhere in the code folder? Let's put a link/note to it here. The aspect ratio of these 3D files should be adjusted such that it faithfully shows the actual geography. That should happen in the function plot3D.x3p.file }}
\end{figure}
Each fired bullet is provided in form of a set of six x3p files, where each file is a surface scan between adjacent grooves on the bullet, called a ``land". An example of plotting one of these lands is given in Figures~\ref{fig:sidex3p} and~\ref{fig:topx3p}, which show side and top profiles of the land respectively.
